Appendix: Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2025-01-17 appendix.qmd
Updated bin circles
Updated Figure 2

```{r}
# all_centroids_df <- gen_centroids(bin1 = 4, r2 = r2, q = 0.1)
# 
# hex_grid <- gen_hex_coord(all_centroids_df, a1 = 1.043789)

## Compute hexbin parameters
num_bins_x_scurve <- 3

@@

## Data to generate circle
circles <- data.frame(
  x = c(0.422, 0.683),
  y = c(0.740, 1.19),
  r = rep(0.301316, 2)
)

emb_df1 <- tibble(emb1 = 0.58, emb2 = 0.93) |>
  add_row(emb1 = 0.5, emb2 = 1.01)

assign_data_vis1 <- ggplot(data = hex_grid, aes(x = x, y = y)) + 
  geom_polygon(fill = "white", color = "#bdbdbd", aes(group = hex_poly_id)) +
  geom_point(data = emb_df1, aes(x = emb1, y = emb2), color = "black", size = 0.7) +
  geom_text(data = all_centroids_df, aes(x = c_x, y = c_y, label = hexID), size = 5, colour = "#bdbdbd") +
  geom_circle(data = circles, aes(x0 = x, y0 = y, r = r), fill = NA) +
  geom_segment(x = 0.58, y = 0.93, xend = 0.44, yend = 0.76, 
               arrow = arrow(length = unit(0.02, "npc")), color = "#969696") +
  geom_segment(x = 0.5, y = 1.01, xend = 0.68, yend = 1.16, 
               arrow = arrow(length = unit(0.02, "npc")), color = "#969696")

>>>>

```{r}
## Compute hexbin parameters
num_bins_x_scurve <- 3

@@

## Data to generate circle
circles <- data.frame(
  x = c(0.726, 0.451),
  y = c(1.27, 0.790),
  r = rep(0.32, 2)
)

emb_df1 <- tibble(emb1 = 0.61, emb2 = 0.99) |>
  add_row(emb1 = 0.54, emb2 = 1.08)

assign_data_vis1 <- ggplot(data = hex_grid, aes(x = x, y = y)) + 
  geom_polygon(fill = "white", color = "#bdbdbd", aes(group = hex_poly_id)) +
  geom_point(data = emb_df1, aes(x = emb1, y = emb2), color = "black", size = 0.7) +
  geom_text(data = all_centroids_df, aes(x = c_x, y = c_y, label = hexID), size = 5, colour = "#bdbdbd") +
  geom_circle(data = circles, aes(x0 = x, y0 = y, r = r), fill = NA) +
  geom_segment(x = 0.61, y = 0.99, xend = 0.46, yend = 0.83, 
               arrow = arrow(length = unit(0.02, "npc")), color = "#969696") +
  geom_segment(x = 0.54, y = 1.08, xend = 0.7, yend = 1.2, 
               arrow = arrow(length = unit(0.02, "npc")), color = "#969696")
